Machine Learning Tools for Open Cluster Characterization with Gaia DR2 Data

### 2021-01-26 paper/paper.tex
paper: Add title, abstract and key words

\documentclass[11pt,a4paper,english,twocolumn]{article}
\usepackage{unir_paper}

%---------------------------
%título del trabajo y autor
%---------------------------
\title{Título}
\author{Nombre y Apellidos del estudiante}
\date{fecha}

@@

\resumen{Breve resumen del trabajo realizado (extensión máxima: 150 palabras). Este resumen debe incluir el objetivo o propósito de la investigación, la metodología, los resultados y las conclusiones.}
\palabrasclave{tres a cinco palabras clave por orden alfabético y separadas por comas}

>>>>

\documentclass[11pt,a4paper,USenglish,twocolumn]{article}
\usepackage{unir_paper}

%---------------------------
%título del trabajo y autor
%---------------------------
\title{Machine Learning Tools for Open Cluster Characterization with Gaia DR2 Data}
\author{Carlos David Álvaro Yunta}
\date{24th of January, 2021}

@@

\resumen{
The characterization and understanding of \emph{Open Clusters}
allow us to better understand properties and mechanisms about the Universe
such as stellar formation and the kind of regions where these events occur.
They also provide information about stellar processes and the evolution of the galactic disk.

In this paper, we develop a method to characterize open clusters by using
\emph{artificial intelligence} tools, such as clustering by \emph{K-Means}
and clustering based on \emph{Artificial Neural Networks} by implementing
the \emph{Deep Embedded Clustering} model.
We are using \emph{Gaia DR2 database} as data source for testing our models.

The developed method aims to improve current techniques of the state of the art.
We achieve improvements not only in terms of \emph{computational efficiency},
with lower computational requirements, but in \emph{usability},
reducing the number of hyperparameters to obtain a good characterization of the analyzed clusters.

Our method achieves good results,
becoming even better in some cases when the results are compared with current techniques.
}

\palabrasclave{
    characterization,
    data analysis,
    deep embedded clustering,
    gaia,
    machine learning,
    open cluster
}
